### 2017-11-21 manuscript.rmd
presence nectophores -> presence nectosome

#####SIMMAP Presence of Nectophores
```{r nectosome, echo=F, message=F, warning=F}
#Simmap NECTOSOME
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nectosome_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
nodelabels(pie=(describe.simmap(nectosome_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(nectosome_sim)
```
Posterior probabilities of states (1 Present, 0 Absent).

>>>>

#####SIMMAP Presence of Nectosome
```{r nectosome, echo=F, message=F, warning=F}
#Simmap NECTOSOME
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nectosome_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
nodelabels(pie=(describe.simmap(nectosome_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(nectosome_sim)
```
Posterior probabilities of states (1 Present, 0 Absent).
